### 2024-08-15 actuarial.qmd
20240814 - shrinkage and cross-validation

@@

In general, there is often shrinkage of estimates from training data set to a test data set.
*Shrinkage* is when variables with stronger predictive power in the original data set tend to show somewhat smaller predictive power (smaller regression coefficients) when applied to new groups.
Shrinkage reflects a model [overfitting](#sec-overfitting) (i.e., fitting to error by capitalizing on chance).
Shrinkage is especially likely when the original sample is small and/or unrepresentative and the number of variables considered for inclusion is large.
Cross-validation with large, representative samples can help evaluate the amount of shrinkage of estimates, particularly for more complex models such as [machine learning](#sec-machineLearning) models [@Ursenbach2019].
Ideally, cross-validation would be conducted with a separate sample (external cross-validation) to see the generalizability of estimates.
However, you can also do internal cross-validation.
For example, you can perform *k*-fold cross-validation, where you:

An emerging technique that holds promise for increasing predictive accuracy of actuarial methods is [machine learning](#sec-machineLearning) [@Garb2019].
However, one challenge of some [machine learning](#sec-machineLearning) techniques is that they are like a "black box" and are not transparent, which raises ethical concerns [@Garb2019].
[machine learning](#sec-machineLearning) may be most valuable when the data available are complex and there are many [predictor variables](#sec-correlationalStudy) [@Garb2019].

>>>>

## Challenges of Data-Driven Approaches and How to Address {#sec-challengesDataDrivenApproaches}

There are various challenges of data-driven approaches.
First, they are sometimes not interpretable or consistent with theory.
Second, they tend to [overfit](#sec-overfitting) the data.
[Overfitting](#sec-overfitting) is described in @sec-overfitting.
Third, as a result of [overfitting](#sec-overfitting) the data, they tend to show [shrinkage](#sec-shrinkage).

### Shrinkage {#sec-shrinkage}

In general, there is often shrinkage of estimates from training data set to a test data set.
*Shrinkage* is when variables with stronger predictive power in the original data set tend to show somewhat smaller predictive power (smaller regression coefficients) when applied to new groups.
Shrinkage reflects a model [overfitting](#sec-overfitting)—i.e., when the model explains error variance by capitalizing on chance.
Shrinkage is especially likely when the original sample is small and/or unrepresentative and the number of variables considered for inclusion is large.
To help minimize the extent of shrinkage, it is recommended to apply [cross-validation](#sec-crossValidation).

### Cross-Validation {#sec-crossValidation}

Cross-validation with large, representative samples can help evaluate the amount of shrinkage of estimates, particularly for more complex models such as [machine learning](#sec-machineLearning) models [@Ursenbach2019].
Ideally, cross-validation would be conducted with a separate sample (external cross-validation) to see the generalizability of estimates.
However, you can also do internal cross-validation.
For example, you can perform *k*-fold cross-validation, where you:

@@

An emerging technique that holds promise for increasing predictive accuracy of actuarial methods is [machine learning](#sec-machineLearning) [@Garb2019].
However, one challenge of some [machine learning](#sec-machineLearning) techniques is that they are like a "black box" and are not transparent, which raises ethical concerns [@Garb2019].
Moreover, [machine learning](#sec-machineLearning) also tends to lead to [overfitting](#sec-overfitting) and [shrinkage](#sec-shrinkage).
[machine learning](#sec-machineLearning) may be most valuable when the data available are complex and there are many [predictor variables](#sec-correlationalStudy) [@Garb2019], and when the model is validated with [cross-validation](#sec-crossValidation).
